---
title: "p8105_hw1_JP3665"
author: "Joana Petrescu"
date: "9/19/2020"
output: github_document
---

# Problem 1

## Create data frame

A random sample of size 10 from standard normal distribution

```{r}

vrandom <- rnorm(10)

```

A logical vector indicating whether elements of sample are greater than 0

```{r}

vlogic <- vrandom > 0

```

A character vector of length 10

```{r}

vcharacter <- c("one", "two", "three", "four", "five", "six", "seven", "eight", "nine", "ten")

```

A factor vector of length 10 with 3 different factor levels

```{r}

vfactor <- factor(c(1,2,3,1,3,1,2,2,3,1), levels = c(1, 2, 3), labels = c("red", "blue", "green"))

```

Make data frame

```{r}

df <- data.frame(vrandom, vlogic, vcharacter, vfactor)
print(df)

```

Take mean of variables

```{r, echo=TRUE, warning=FALSE}

mean(vrandom)

mean(vlogic)

mean(vcharacter)

mean(vfactor)

```

_You can only take the mean of vectors that are numeric or logical, not character or factor vectors_

## Convert vector types

```{r, echo=TRUE, results=FALSE, warning=FALSE}

as.numeric(vlogic)

as.numeric(vcharacter)

as.numeric(vfactor)

```

```{r, echo=TRUE}

mean(as.numeric(vfactor))

```

_Logical vectors can be converted to numeric (0 for false, 1 for true), character vectors return "NA" when coerced to numeric type, and factors can be converted to numeric based on the defined levels. I was curious whether you could take the mean of a factor vector once you convert it to numeric and it turns out that you can._

```{r, echo=TRUE}

numlogic <- as.numeric(vlogic)

numlogic * vrandom

factlogic <- as.factor(vlogic)

factlogic * vrandom

as.numeric(factlogic) * vrandom

```

# Problem 2

About the `penguins` dataset

```{r, echo=TRUE}

data("penguins", package = "palmerpenguins")

colnames(penguins)

levels(penguins$species)

levels(penguins$island)

nrow(penguins)

ncol(penguins)

mean(penguins$flipper_length_mm)

```

Plot flipper length

```{r}

library(ggplot2)

ggplot(penguins, aes(x=bill_length_mm, y=flipper_length_mm, color = species)) + geom_point(shape=19)

ggsave

```


